---
title: "Twitter-Based Economic Policy Uncertainty Index for Chile∗"
author:
  - Sebastian Becerra^[Central Bank of Chile, seba.becerra@gmail.com]
  - Andrés Sagner^[Central Bank of Chile, asagner@bcentral.cl]

date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
---



```{r include=FALSE}
#instalamos los paquetes si hace falta
if(!require("tidyverse")) install.packages("tidyverse")
if(!require("fs")) install.packages("fs")
if(!require("readxl")) install.packages("readxl")


#paquetes
library(plotly)
library(tidyverse)
library(fs)
library(readxl)
```

<font size="3" color="black"><p style="text-align:justify;">
In this paper, we develop a daily-frequency measure of economic uncertainty for
Chile employing information that was obtained from Twitter accounts using web scrap-ing techniques and following closely the methodology proposed by Baker et al. (2016). Our proposed measures, called DEPU and DEPUC, aim to capture the level of general disagreement —a proxy for economic uncertainty— in topics such as the economy, economic policies, uncertainty about particular events, and the current economic situation in Chile. Both indices, available from 2012 onwards, show significant hikes that coincide with several local and international episodes that provoked extraordin ary levels of economic uncertainty in Chile, especially after the events around the civil protests in mid-October 2019 and the COVID-19 pandemic in mid-March 2020. An empirical exercise reveals that the proposed measures are significant determinants of the nominal exchange rate dynamics, especially when the magnitude of this variable is high and a week after the shock occurs. When the exchange rate is low, on the contrary, the impact of uncertainty on this variable is quantitatively smaller for any forecasting hori-
zon. These features, and others discussed in the paper, highlight the usefulness of the proposed metric as an additional indicator that policymakers can incorporate into their monitoring toolkit.
</p></font>

[Data](https://drive.google.com/file/d/1wvkhsr4xhku2cWlKzK-r0CtDMPvtDkFJ/view?usp=sharing) 
<br>
<!-- [Paper](https://drive.google.com/file/d/1lLixKTiuunU0tAJz38YPS9mW4sT7QqNr/view?usp=sharing) -->
[Paper](https://www.bcentral.cl/documents/33528/133326/dtbc883.pdf/ad65f9fd-c263-a5a5-ba2c-eb9af6c2c7ce?t=1595449144477)

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = 'center', out.width = '100%'}
path="D:/Trabajo/twitter/DEPUC/basededatos/"
depu<-read_excel(paste0(path,"DEPUC.xls"),2)
depu$week=stringi::stri_datetime_fields(depu$date)$WeekOfMonth
imacec<-read_excel(paste0(path,"DEPUC.xls"),"imacec")
depu <- merge(depu, imacec, by=c("anio", "mes","dia"), all=T)
```

<br>
<center>
<font size="4" color="black"><p style="text-align:center;">Daily Economic Policy Uncertainty Measures (\*)<br><font size="2" color="black"></font></p></font>
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = 'center', out.width = '100%'}

fig1 <- plot_ly(depu, y =~depu_ma_30, x=~date, name = 'DEPU', type = 'scatter', mode="lines" ,line = list(color = "blue", width = 4), hoverinfo = 'text', text = ~paste('</br> date: ', format(date, "%d%b%Y"),
                      '</br> Valor: ', format(round(depu_ma_30, 2),nsmall=2)))  %>% add_trace(y = ~depuc_ma_30, x=~date, name = 'DEPUC', type="scatter", mode="lines", line = list(color = "orange", width = 4),hoverinfo = 'text', text = ~paste('</br> Fecha: ', format(date, "%d%b%Y"),'</br> Valor: ', format(round(depuc_ma_30,2),nsmall=2))) %>% layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, y=1), xaxis = list(title = "", showgrid = F,  type="date", tickangle=0, showline = F, tick0="2012-01-01", dtick="M12",  tickformat="<br>%y",range=c("2011-11-01","2020-08-31"),rangeslider = list(type = "date")),yaxis = list(title = " ", side="left",range=c(-1,3),dtick=1,showgrid = F,zerolinecolor ="black", zerolinewidth = 1.5, zeroline = T, ticksuffix=" ", tickformat = ".1f"),                            shapes=list(list(type='line', x0= "2012-01-16", x1= "2012-01-16", y0=-1, y1=3, line  =list (dash='dot', width=4, color="gray"), opacity = 0.3),
list(type='line', x0= "2012-04-30", x1= "2012-05-05", y0=-1, y1=3, line=list(dash='dot', width=4, color="gray"), opacity = 0.3),
list(type='line', x0= "2013-06-30", x1= "2013-06-21", y0=-1, y1=3, line=list(dash='dot', width=4, color="gray"), opacity = 0.3),
list(type='line', x0= "2013-11-21", x1= "2013-11-21", y0=-1, y1=3, line=list(dash='dot', width=4, color="gray"), opacity = 0.3),
list(type='line', x0= "2014-05-14", x1= "2014-05-14", y0=-1, y1=3, line=list(dash='dot', width=4, color="gray"), opacity = 0.3),
list(type='line', x0= "2014-09-10", x1= "2014-09-10", y0=-1, y1=3, line=list(dash='dot', width=4, color="gray"), opacity = 0.3),
list(type='line', x0= "2017-12-31", x1= "2017-12-31", y0=-1, y1=3, line=list(dash='dot', width=4, color="gray"), opacity = 0.3),
list(type='line', x0= "2018-06-16", x1= "2018-06-16", y0=-1, y1=3,   line=list(dash='dot', width=4, color="gray"), opacity = 0.3),
list(type='line', x0= "2019-06-15", x1= "2019-06-15", y0=-1, y1=3, line=list(dash='dot', width=4, color="gray"), opacity = 0.3),
list(type='line', x0= "2020-01-22", x1= "2020-01-22", y0=-1, y1=3, line=list(dash='dot', width=4, color="gray"), opacity = 0.3),
list(type="rect", fillcolor="gray", line = list(color = "white"),x0="2019-10-20", x1="2020-01-01", y0=-1, y1=3, opacity=0.4, layer="below"),
list(type="rect", fillcolor="gray", line = list(color = "white"),x0="2020-03-10", x1="2020-06-26", y0=-1, y1=3, opacity=0.4, layer="below")), 
annotations = list(list(text = "European<br>debt crisis",  x = "2012-01-16", y = 0.7,showarrow=T, xanchor="left"),list( text="Tax reform proj.<br>announcement", x="2012-04-30", y=2, showarrow=T, xanchor="rigth"),list(text = "Primaries<br>elections",  x = "2013-06-30", y = 1.5,showarrow=T, xanchor="left"),list(text = "Runoff<br>elections",  x = "2013-11-21", y = 0.8,showarrow=T, xanchor="left"),list(text = "Tax reform<br>approval",  x = "2014-05-14", y = 1.5,showarrow=T, xanchor="left"),list(text = "Explosive attack<br>Santiago subway",  x = "2014-09-10", y = 1,showarrow=T, xanchor="left"),list(text = "Runoff<br>elections",  x = "2017-12-31", y = 0.5,showarrow=T, xanchor="left"),list(text = "China-US<br>trade war",  x = "2018-06-16", y = 1.2,showarrow=T, xanchor="left"),list(text = "CLP/USD<br>700",  x = "2019-06-15", y = 0.7,showarrow=T, xanchor="rigth")
,list(text = "O-18",  x = "2019-12-01", y = 1.1,showarrow=T, xanchor="rigth"),list(text = "Wuhan under<br>quarantine",  x = "2020-01-24", y = 1.6,showarrow=T, xanchor="rigth"),list(text = "",  x = "2020-07-1", y = 0.4,showarrow=T, xanchor="rigth", ax=0,ay =40),list(text = "<br>IMACEC",  x = "2020-05-25", y = 0.15,showarrow=T, xanchor="rigth", ax=0,ay =30),list(text = "10%",  x = "2020-07-08", y = 0.7,showarrow=T, xanchor="rigth"))) %>% config(modeBarButtonsToRemove = c("zoom2d", "pan2d", "select2d", "lasso2d", "zoomIn2d", "zoomOut2d", "autoScale2d", "resetScale2d", "hoverClosestCartesian", "hoverCompareCartesian", "zoom3d", "pan3d", "resetCameraDefault3d", "resetCameraLastSave3d", "hoverClosest3d", "orbitRotation", "tableRotation", "zoomInGeo", "zoomOutGeo", "resetGeo", "hoverClosestGeo", "sendDataToCloud", "hoverClosestGl2d", "hoverClosestPie", "toggleHover", "resetViews", "toggleSpikelines", "resetViewMapbox"),displaylogo = FALSE)
fig1
```
</center>
<font size="2"><p>(\*) Both series were filtered using a 30-days moving average to avoid excessive daily variability. Vertical lines mark events of substantial economic uncertainty, whereas shaded areas mark various events related to the civil protests and riots of October 2019 and the COVID-19 pandemic starting mid-March 2020 onwards.<br>
Source: Authors’ elaboration.</p></font>

<br>
<center>
<font size="4" color="black"><p style="text-align:center;">Daily Economic Policy Uncertainty Measures & IMACEC(\*)<br><font size="2" color="black"></font></p></font>
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align = 'center', out.width = '100%'}

fig1 <- plot_ly(depu, y =~depu_ma_30, x=~date, name = 'DEPU', type = 'scatter', mode="lines" ,line = list(color = "blue", width = 4), hoverinfo = 'text', text = ~paste('</br>Fecha: ', format(date, "%d%b%Y"), '</br> Valor: ', format(round(depu_ma_30, 2),nsmall=2)))  %>% add_trace(y = ~depuc_ma_30, x=~date, name = 'DEPUC', type="scatter", mode="lines", line = list(color = "orange", width = 4),hoverinfo = 'text', text = ~paste('</br> Fecha: ', format(date, "%d%b%Y"),'</br> Valor: ', format(round(depuc_ma_30,2),nsmall=2))) %>% add_trace(y = ~imacecv12, name = 'IMACEC (RA)', type="scatter", mode="markers", line = list(color = "green", width = 4), hoverinfo = 'text', text = ~paste('</br>Fecha: ', format(date, "%b%Y"), '</br> IMACEC: ', format(round(imacecv12, 2),nsmall=2)), yaxis="y2") %>% layout(legend = list(orientation = "h", xanchor = "center", x = 0.5, y=1), xaxis = list(title = "", showgrid = F,  type="date", tickangle=0, showline = F, tick0="2012-01-01", dtick="M12",  tickformat="<br>%y",range=c("2011-11-01","2020-07-31"),rangeslider = list(type = "date")),yaxis = list(title = " ", side="left",range=c(-3,3),dtick=1,showgrid = F,zerolinecolor ="black", zerolinewidth = 1.5, zeroline = T, ticksuffix=" ", tickformat = ".0f"), yaxis2 = list(title = " ", side="right",range=c(-18,18), dtick=6,showgrid = F,zerolinecolor ="black", zerolinewidth = 1.5, zeroline = T, tickformat = ".0f", overlaying = "y", automargin=T)) %>% config(modeBarButtonsToRemove = c("zoom2d", "pan2d", "select2d", "lasso2d", "zoomIn2d", "zoomOut2d", "autoScale2d", "resetScale2d", "hoverClosestCartesian", "hoverCompareCartesian", "zoom3d", "pan3d", "resetCameraDefault3d", "resetCameraLastSave3d", "hoverClosest3d", "orbitRotation", "tableRotation", "zoomInGeo", "zoomOutGeo", "resetGeo", "hoverClosestGeo", "sendDataToCloud", "hoverClosestGl2d", "hoverClosestPie", "toggleHover", "resetViews", "toggleSpikelines", "resetViewMapbox"),displaylogo = FALSE) 

fig1
```
</center>
<font size="2"><p>(\*) DEPU & DEPUC series were filtered using a 30-days moving average to avoid excessive daily variability. <br>
(\*) IMACEC montly and right axis.<br>
Source: Authors’ elaboration.</p></font>

